COG-ED Manuscript

### 2021-11-15 06_Paper/COG-ED/Manuscript.Rmd
re-included data frame "data_RT"

@@

## Analysis
We aimed to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
Error- and post-error trials were excluded, because RT on the latter trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
#TODO: Tolle Artikel, die schaue ich mir auch noch mal genauer an! Hast du die beiden exclusions schon im script umgesetzt? Falls ja, in welcher Zeile, ich kann es nicht finden...
Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was examined using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
And the last regression **insert method**.

@@

```{r Hypothesis_3c, echo=FALSE, message=FALSE, warning=FALSE}

  # H3c: When putting the SVs in descending order before computing the AUC, the prediction of NFC scores by SVs can be improved significantly.

  h3c_data <- data.frame(subject = character(), auc_sv_sorted = double())

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv_sorted = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = TRUE))
    h3c_data <- rbind(h3c_data, newdata)

  h3_data <- merge(h3_data, h3c_data)

  # remove temporary variable

  remove(h3c_data)

  # compute linear regression to predict NCS based on SV AUC

  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv_sorted))

>>>>

  # remove trials with RT < 200 ms from the n-back data and exclude trials after incorrect trials
  data_RT <- data_nback[-c(which(data_nback$rt < 0.2)), ]
  data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]

@@

## Analysis
We aimed to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Whelan2008; @Berger2021].
Error- and post-error trials were excluded, because RT on the latter trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was examined using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
And the last regression **insert method**.

@@
